Variational Monte Carlo on bosonic systems

### 2018-03-08 project_1/article/article.tex

>>>>

        INSERT PSEUDO-CODE DESCRIPTION OF

\section{Results}

	\subsection{Non-Interacting Systems}
	Initially we are interested in seeing how our implementation performs and to what extent it functions properly.
	the logical thing to do would be to look at a non-interacting system with a simple Gaussian wavefunction and
	harmonic oscillator potential. Such a system has a simple closed-form analytic solution\footnote{A fact that every 
	undergraduate physics student should be well aware of.}.
